Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-04-30 Ben_Manuscripts/structure_paper/Outline.tex
Outline updates and new figures

  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
  into stacked layers which form columnar pores. 
%BJC: commenting out :There has been no definitive answer in literature regarding the number of monomers in each layer. 
%MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers. Can you rephrase so it's more general? Maybe just take out that sentence above.
We want to know 
\begin{enumerate}
\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
  \begin{itemize}
    \item A simple molecular simulation study of a similar molecule suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model orders of magnitude larger than any other reported atomistic 
    liquid crystal membrane simulations has the best chance of directly answering this question.
    \item We can directly change the layer composition and note its effect on membrane structure.
  \end{itemize}

 \item Does our model support the existence of layers and if so, how well defined
  are the layers? \label{point:layers}
  \begin{itemize}
       \item Experimentally, their existence is supported by evidence of strong 
       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
       membrane plane.
       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
       leaves no description of what is happening in the monomer tail region
       \item The tails may entangle isotropically while stacking order is maintained
       among headgroups. 
  \end{itemize}

   \item How do monomers in each layer position themselves with respect to surrounding 
   layers? \label{point:orientation}
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
   \begin{itemize}
      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
      \item We can use simulated X-ray diffration patterns to compare the two 
      stacking configurations. 
   \end{itemize}

  \item Can the system exist in other metastable states or phases that are not
  accessed during experiments? \label{point:metastable}
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally and 
    why others are not.
  \end{itemize}

  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
  \begin{itemize}
	\item The limited picture that experiment provides tells us that there are
        hexagonally packed, hydrophilic regions where transport is likely to occur
	\item One may instinctively assume that these regions are tube-like pathways
	\item We will explore the composition of the pores and the partition
	between the hydrophilic and hydrophobic regions. 
  \end{itemize}

  \item Is it necessary to include any water in order to appropriately model the 
  Col\textsubscript{h} phase? \label{point:water}
  \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
          %MRS3: ``possible'' -> likely, and give some explanations why we think likely? 
	likely that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
  \end{itemize}
  \end{enumerate}

  %Once we have addressed all of the above questions, we must show that the 
  %developed molecular model is consistent with physical observations so that we
  %can rely on conclusions drawn about structural features characteristic of 
  %the system.

@@

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.  You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.  
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
  		\item We built systems in both the parallel displaced and sandwiched configurations and
  		equilibrated them according to the dry equilibration procedure.
  		\item We test all systems with an initial layer spacing, l, of 3.7 \AA.
  		\item We tested 4 additional systems with layers initially spaced 5 \AA~apart (See 
  		supporting info for more details on sensitivity to initial layer spacing)
  		\item The pore-to-pore spacing is stable in all systems after 400 ns of simulation. 
  		Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems 
  		tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
	    \item comment about disordered systems
  \end{itemize}

@@

  % BJC4: I will add 6 mon/layer disordered data once I have it.
  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm, regardless of initial layer spacing, l. The 
			 equilibrated pore spacing of the model increases as the number of monomers 
			 in each layer increases. The pore spacing of systems starting in the sandwiched 	
			 configuration are systematically lower than those started in the parallel 
			 displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. 
  \begin{itemize}
	  	\item We tested systems built with 5 monomers per layer in the parallel 
		displaced and sandwiched configurations at 300 K with layers initially spaced
		3.7 \AA and 5.0 \AA apart.
		\item We generated simulated patterns using portions of simulation trajectory
		after equilibration.
		\item The patterns for all structures are shown and compared to experiment
		in Figure~\ref{fig:XRDsim}.
  \end{itemize}

@@

%BJC4: I'm not sure what the best way to set up this figure is yet.
  \begin{figure}[htb]
	\centering
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	        		\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet.png}
			        \caption{Sanwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}

@@

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
    %MRS4: we will need to provide more details: more intense is just qualiatative.
    %BJC4: I can include the intensity of the first peak of R-pores in the tables that 
    % show relative intensities.
  		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
    %BJC4: So a combo of: domain misalignment, slow dynamics of simulated system, only 4 pores
    % in unit cell, tortuosity (?)
    	\item R-spots appears to be weaker in the simulated patterns. They are also partially 
	    engulfed by the wide R-$\pi$ reflection.
	    \item We further explore R-spots in Section~\ref{section:rspots}  
        \item R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the
	    reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers
	    prefer stack greater than 4.2 \AA apart rather than 3.7 \AA. This behavior is not
	    surprising since GAFF models atoms as point charges and does not appropriately model 
	    the aromatic $\pi-\pi$ interactions which would cause the monomers to stack closer
	    together.
	    \item We will explore R-$\pi$ in more detail in Section~\ref{section:rpi}.
            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
			%BJC: Might have something to do with the distibution of tilt angles in the tails
	    \item R-double does not appear in any of the patterns
	    \item We will explore its possible origins and reasons that it does not appear in our
	    simulated patterns in Section~\ref{section:rdouble}.
  \end{itemize}

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. 
  \begin{itemize}
  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
  		the $q_z$ value of R-$\pi$. 
  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
  		appear for the same reason as R-double. 
  		\item This type of pattern is characteristic of a helix (reference something)
  		\item It is possible that these reflections contribute to the continuation of
  		R-double into R-alkanes, as seen in the experimental pattern. 
  \end{itemize}

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  \begin{itemize}
  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
  		of each reflection for each system tested.
  		\item The patterns are normalized so that the average intensity of R-alkanes equals 1. 
  		% BJC4: I need to explain how I calculated these intensities somewhere. Is this the right
  		% place to do it? I think it would just be confusing in the methods. I could also move it
  		% to supplemental.
  		\item We measured the approximate intensity of R-$\pi$ by measuring the intensity of 
  		the peak of the cross-section at $q_r=0$. 
  		\item The relative intensity of R-$\pi$ is significantly higher than experiment in our
  		simulations.
  		\item R-spots is measured as the average intensity within the region bounded by a 'spot'.
  		Spots are identified based on visual inspection. If there is no easily discernable spot,
  		then the intensity is taken as that of the intersection of R-alkanes at half the $q_z$
  		value of R-$\pi$, since that is where it appears experimentally. 
  		\item The intensity of R-spots is slightly lower than experiment in all cases.
  		\item There is no R-double intensity to be measured.
  \end{itemize}

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. 
  \begin{itemize}
  		\item R-spots is most intense in the sandwiched configuration
  		(Figure~\ref{fig:sandwiched280K}).
  		\item The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3) 
  		\item Still no R-double
  		\item We can use this configuration to more thoroughly explore the origin of R-spots.
  \end{itemize}

@@

   %BJC4: include dashed line at mean. 
  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle is near 7\degree~which is far from the
	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  %BJC: modification of above paragraph to only include 280K sandwiched data
  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
  performed the same integration on the raw experimental data and found the angle
  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
  is a reconcilable difference with our simulated results.

@@

  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
  experimental conditions of 300 K.
  \begin{itemize}
  		\item (1) The difference between 280K and 300K is small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300K (citation?).
  		\item (2) Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{itemize}

@@

  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure reference).
  \begin{itemize}
  		\item We averaged all 1D slices in the z-direction of the full 3D correlation function
  		within 2.1 \AA of $(x, y)=(0, 0)$. (full description will be in methods)
  		\item We chose 2.1 \AA as a crude approximation of the radius of the phenyl ring
  		plane. 
  		\item We calculated it as the sum of the longest C-C distance within a phenyl 
  		ring (2.8 \AA) and two times the carbon atom radius (0.7 \AA).
  \end{itemize}

  %BJC4: the correlation functions of disordered systems are confusing me.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{}\label{fig:correlation}
  \end{figure}

  The correlation length between stacked monomer head groups shows the best agreement with
  experimental for systems simulated at 300K.
  %BJC3: explanation of correlation length calculation in methods section. 
  \begin{itemize}
  		\item Correlation length was calculated by fitting a decaying exponential function
  		to all peaks of $g(z)$ for the sandwiched configuration and to every other peak of
  		$g(z)$ for the parallel displaced configuration. 
  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
  		for the parallel displaced and sandwiched configurations respectively. 
  		\item The correlation length of systems simulated at 300K were 11.2 \AA and 14.9 \AA
  		for the parallel displaced and sandwiched configurations respectively. 
  		\item Systems simulated at 300K show correlation closest to the experimental 
  		correlation length of 10.1 \AA. They are still slightly more correlated than 
  		experiment which would lead to an increase in constructive X-ray scattering. 
  \end{itemize}

>>>>

%  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
%  into stacked layers which form columnar pores. 
%BJC: commenting out :There has been no definitive answer in literature regarding the number of monomers in each layer. 
%MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers. Can you rephrase so it's more general? Maybe just take out that sentence above.
%We want to know 
%\begin{enumerate}
%\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
%    \item A simple molecular simulation study of a similar molecule suggested
%    that there are 4 monomers in each layer. Their estimation is based on a
%    simulated system containing only 16 total monomers which likely does not sufficiently
%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
%    \item A molecular model orders of magnitude larger than any other reported atomistic 
%    liquid crystal membrane simulations has the best chance of directly answering this question.
%    \item We can directly change the layer composition and note its effect on membrane structure.
% \item Does our model support the existence of layers and if so, how well defined
%  are the layers? \label{point:layers}
%       \item Experimentally, their existence is supported by evidence of strong 
%       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
%       membrane plane.
%       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
%       leaves no description of what is happening in the monomer tail region
%       \item The tails may entangle isotropically while stacking order is maintained
%       among headgroups. 
%   \item How do monomers in each layer position themselves with respect to surrounding 
%   layers? \label{point:orientation}
%%     Even if we knew the number of monomers in each layer, we still would not know how 
%%     monomers in each layer are positioned with respect to other layers. 
%      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
%      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
%      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
%      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
%      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
%      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
%      attraction which favors the parallel displaced configuration in all cases
%      except where the substitutions are extremely electron withdrawing
%      \cite{waller_hybrid_2006,ringer_effect_2006}.
%      \item We can use simulated X-ray diffration patterns to compare the two 
%      stacking configurations. 
%  \item Can the system exist in other metastable states or phases that are not
%  accessed during experiments? \label{point:metastable}
%  There remains the possibility that there is more than one metastable state 
%  associated with a given LLC system.
%    \item Simulating a membrane atomistically will require many atoms which further
%    limits the timescales acessible with MD
%    \item It is reasonable to expect that we will generate configurations which 
%    are kinetically trapped in a metastable free energy basin
%    \item We must be able to identify which state is produced experimentally and 
%    why others are not.
%  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
%	\item The limited picture that experiment provides tells us that there are
%        hexagonally packed, hydrophilic regions where transport is likely to occur
%	\item One may instinctively assume that these regions are tube-like pathways
%	\item We will explore the composition of the pores and the partition
%	between the hydrophilic and hydrophobic regions. 
%  \item Is it necessary to include any water in order to appropriately model the 
%  Col\textsubscript{h} phase? \label{point:water}
%	\item While the Col\textsubscript{h} phase is described as dry, it is 
%          %MRS3: ``possible'' -> likely, and give some explanations why we think likely? 
%	likely that small amounts of ambient water may be leached into the system.
%	\item The hydrogen bonding network formed by the water may play a role 
%        in structuring the pore.
%	\item We can use simulated X-ray diffraction patterns to see if there is
%        any meaningful structural difference between a "dry" and "wet" system
%  \end{enumerate}
  %Once we have addressed all of the above questions, we must show that the 
  %developed molecular model is consistent with physical observations so that we
  %can rely on conclusions drawn about structural features characteristic of 
  %the system.

  %BJC4: Consolidation of points into 4 main questions to answer
  There are a number of structural questions we wish to answer in this article. We
  want to know:
  \begin{enumerate}
    \item What is the density of monomers that pack around each hydrophilic core? 
    \label{point:monomernum}
 	\begin{itemize}
 		\item Authors often describe this and similar systems as being made up of layers.
 		\item A simple molecular simulation study of a similar molecule suggested
	    that there are 4 monomers in each layer. Their estimation is based on a
	    simulated system containing only 16 total monomers which likely does not sufficiently
	    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
	    \item A separate calculation based on the volume of the liquid crystal monomers proposes
	    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
 		\item We are careful to avoid the term 'layers' since a liquid crystalline system has,
 		by definition, long range order in 1 or 2 spatial dimensions and short range order in 	
 		the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 		\item In the system we are studying, there are long-range 2D correlations in the 
 		hexagonal array of pores and short range correlations in the z-direction.
		\item We will use our atomistic molecular model to study how the system's structure is
		effected by the density of monomers surrounding each pore's hydrophilic core. 
	\end{itemize}
	\item What structural motif best matches experimental 2D WAXS patterns?\label{point:xrdmatch}
	\begin{itemize}
		\item On the short timescales accessible to MD, we observe distinct metastable 
		configurations which are dependent on starting configuration.
		\item We simulate XRD patterns of our system and compare them to experimental 2D WAXS 
		patterns so that we ensure our model creates a nanoscopic chemical environment maximally
		consistent with experiment within the constraints of our forcefield.
		\item We are able to confirm and refute previous interpretations of the WAXS pattern.  
	\end{itemize}
	\item What is the chemical composition of the pores?\label{point:composition}
	\begin{itemize}
		\item The limited picture that experiment provides tells us that there are
        hexagonally packed, hydrophilic regions where transport is likely to occur
		\item One may instinctively assume that these regions are tube-like pathways with 
		well-defined boundaries.
		\item We will explore the composition of the pores, the partition
		between the hydrophilic and hydrophobic regions, and its sensitivity to initial
		configuration. 
	\end{itemize}
    \item Is it necessary to include any water in order to appropriately model the 
    Col\textsubscript{h} phase? \label{point:water}
    \begin{itemize}
		\item While the Col\textsubscript{h} phase is described as dry, it is likely that small 
		amounts of ambient water may be leached into the system.
		\item The hydrogen bonding network formed by the water may play a role in structuring the
		pore.
		\item We can use simulated X-ray diffraction patterns to see if there is any meaningful 
		structural difference between a "dry" and "wet" system
    \end{itemize}
  \end{enumerate}

@@

  \subsection{Density of monomers around pores}
  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.  You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.  
  %BJC4: Can I support this by plotting the density of head groups axially and show that the peaks are wide/noisy?
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  		\item We built systems in both the parallel displaced and sandwiched configurations and
  		equilibrated them according to the dry equilibration procedure.
  		\item We test all systems with an initial layer spacing, l, of 3.7 \AA.
  		\item We tested 4 additional systems with layers initially spaced 5 \AA~apart (See 
  		supporting info for more details on sensitivity to initial layer spacing)
  		\item The pore-to-pore spacing is stable in all systems after 400 ns of simulation. 
  		Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all systems 
  		tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
	    \item comment about disordered systems
  \end{itemize}

@@

  % BJC4: I will add 6 mon/layer disordered data once I have it. The 6 mon/layer I have was
  % equilibrated differently (layers initially spaced 10 \AA apart and jumped straight into
  % npt), and only for sandwiched config. I have parallel displaced and sandwiched 6mon/layer
  % running currently.
  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm, regardless of initial layer spacing, l. The 
			 equilibrated pore spacing of the model increases as the number of monomers 
			 in each layer increases. The pore spacing of systems starting in the sandwiched 	
			 configuration are systematically lower than those started in the parallel 
			 displaced configuration.}~\label{fig:p2p}
  \end{figure}

@@

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. 
  \begin{itemize}
	  	\item We tested systems built with 5 monomers per layer in the parallel 
		displaced and sandwiched configurations at 300 K with layers initially spaced
		3.7 \AA~and 5.0 \AA~apart.
		\item We generated simulated patterns using portions of simulation trajectory
		after equilibration.
		\item The patterns for all structures are shown and compared to experiment
		in Figure~\ref{fig:XRDsim}.
  \end{itemize}

@@

%BJC4: I'm not sure what the best way to set up this figure is yet.
  \begin{figure}[htb]
	\centering
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet.png}
	        		\caption{Experimental WAXS}~\label{fig:offset_tails}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet.png}
			        \caption{Sandwiched}~\label{fig:rzplot_layered_300K}
			\end{subfigure}

@@

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
    %MRS4: we will need to provide more details: more intense is just qualiatative.
    %BJC4: I can include the intensity of the first peak of R-pores in the tables that 
    % show relative intensities.
  		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
    %BJC4: So a combo of: domain misalignment, defects, slow dynamics of simulated system, only 4 
    %pores in unit cell, tortuosity (?)
    	\item R-spots appears to be weaker in the simulated patterns. They are also partially 
	    engulfed by the wide R-$\pi$ reflection.
	    \item We further explore R-spots in Section~\ref{section:rspots}  
        \item R-$\pi$ appears at a lower $q_z$ value than experiment. In all systems, the
	    reflection reaches its maximum at $q_z < 1.5 \AA^{-1}$ which means that monomers
	    prefer stack greater than 4.2 \AA~apart rather than 3.7 \AA. This behavior is not
	    surprising since GAFF models atoms as point charges and does not appropriately model 
	    the aromatic $\pi-\pi$ interactions which would cause the monomers to stack closer
	    together.
	    \item We will explore R-$\pi$ in more detail in Section~\ref{section:rpi}.
            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
			%BJC4: Might have something to do with the distibution of tilt angles in the tails
	    \item R-double does not appear in any of the patterns
	    \item We will explore its possible origins and reasons that it does not appear in our
	    simulated patterns in Section~\ref{section:rdouble}.
  \end{itemize}

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. 
  \begin{itemize}
  		\item There are horizontal reflections at $|q_z|= 0.7~\AA^{-1}$, exactly half of 
  		the $q_z$ value of R-$\pi$. 
  		\item The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not
  		appear for the same reason as R-double. 
  		\item This type of pattern is characteristic of a helix (reference something)
  		\item It is possible that these reflections contribute to the continuation of
  		R-double into R-alkanes, as seen in the experimental pattern. 
  \end{itemize}

  %BJC4: This paragraph might fit better before qualitative description
  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  \begin{itemize}
  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
  		of each reflection for each system tested.
  		\item The patterns are normalized so that the average intensity of R-alkanes equals 1. 
  		% BJC4: I need to explain how I calculated these intensities somewhere. Is this the right
  		% place to do it? I think it would just be confusing in the methods. I could also move it
  		% to supplemental.
  		\item We measured the approximate intensity of R-$\pi$ by measuring the intensity of 
  		the peak of the cross-section at $q_r=0$. 
  		\item The relative intensity of R-$\pi$ is significantly higher than experiment in our
  		simulations.
  		\item R-spots is measured as the average intensity within the region bounded by a 'spot'.
  		Spots are identified based on visual inspection. If there is no easily discernable spot,
  		then the intensity is taken as that of the intersection of R-alkanes at half the $q_z$
  		value of R-$\pi$, since that is where it appears experimentally. 
  		\item The intensity of R-spots is slightly lower than experiment in all cases.
  		\item There is no R-double intensity to be measured.
  \end{itemize}

@@

  We observe an increase in the intensity of R-spots when we simulate systems at 280K. 
  \begin{itemize}
  		\item R-spots is most intense in the sandwiched configuration
  		(Figure~\ref{fig:sandwiched280K}).
  		\item The relative intensity of R-spots is higher than in experiment (1.5 vs. 1.3) 
  		\item Still no R-double
  		%BJC4: I think the following is a reasonable thing to do. Use a configuration that really
  		% exhibits R-spots so we can definitively (as best as possible anyways) prove its origin. 
  		% Otherwise, we will have to go off the 300K data which isn't as clear cut. 
  		\item We can use this configuration to more thoroughly explore the origin of R-spots.
  \end{itemize}

@@

   %BJC4: include dashed line at mean. 
  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle (dashed line) is near -2\degree~which is far from 
	  the 37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  %BJC: modification of above paragraph to only include 280K sandwiched data
  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figure \ref{fig:layered_tails} 
  are located at $\pm 33 \degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe that distinct peaks appear c.a. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figure~\ref{fig:layered_integration}). We
  performed the same integration on the raw experimental data and found the angle
  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
  is a reconcilable difference with our simulated results.

@@

  There are a couple reasons why we see stronger ordered chain packing at 280 K compared to
  experimental conditions of 300 K.
  \begin{enumerate}
  		\item The difference between 280K and 300K is small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300K (citation?).
  		\item Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{enumerate}

@@

  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure~\ref{fig:correlation}).
  \begin{itemize}
  		\item We averaged all 1D slices in the z-direction of the full 3D correlation function
  		within 2.1 \AA of $(x, y)=(0, 0)$. (full description will be in methods)
  		\item We chose 2.1 \AA as a crude approximation of the radius of the phenyl ring
  		plane. 
  		\item We calculated it as the sum of the longest C-C distance within a phenyl 
  		ring (2.8 \AA) and two times the carbon atom radius (0.7 \AA).
  \end{itemize}

  %BJC4: the correlation functions of disordered systems are confusing me.
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_sandwich.png}
  \caption{}\label{fig:z_correlation_sandwich}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{z_correlation_offset.png}
  \caption{}\label{fig:z_correlation_offset}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  %BJC4: This is noisier than l=3.7 angstrom, but I can still pick out peaks. I'm unsure
  % how to quantify the difference. The correlation length is very similar to the more
  % ordered configuration.
  \includegraphics[width=\textwidth]{z_correlation_sandwich_disordered.png}
  \caption{}\label{fig:z_correlation_sandwich_disordered}
  \end{subfigure}  
  \begin{subfigure}{0.45\textwidth}
  \centering
  %BJC4: There really aren't any good peaks here. 
  \includegraphics[width=\textwidth]{z_correlation_offset_disordered.png}
  \caption{}\label{fig:z_correlation_offset_disordered}
  \end{subfigure}  
  \caption{}\label{fig:correlation}
  \end{figure}

%  The correlation length between stacked monomer head groups shows the best agreement with
%  experimental for systems simulated in the ordered basin.
%  %BJC3: explanation of correlation length calculation in methods section. 
%  \begin{itemize}
%  		\item Correlation length was calculated by fitting a decaying exponential function
%  		to all peaks of $g(z)$ for the sandwiched configuration and to every other peak of
%  		$g(z)$ for the parallel displaced configuration. 
%%  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
%%  		for the parallel displaced and sandwiched configurations respectively. 
%  		\item The correlation length of systems simulated in the ordered basin were 11.2 \AA and 
%  		14.9 \AA  		for the parallel displaced and sandwiched configurations respectively. 
%  		\item Systems simulated at 300K show correlation closest to the experimental 
%  		correlation length of 10.1 \AA. They are still slightly more correlated than 
%  		experiment which would lead to an increase in constructive X-ray scattering. 
%  \end{itemize}
